### 2020-12-10 exploratory/2020-11/plots.Rmd
Plot fraction mapped with open-ref as sanity check

It looks like one result per parameter set is left over from before I re-ran 
everything after revering to the older silva version.
[Here's what the plot looked like with the newest (buggy) silva](https://github.com/SchlossLab/OptiFitAnalysis/blob/master/exploratory/2020-05/sub3_fit_all-seqs.md#fraction-of-sequences-that-map-to-the-reference).
Need to go back and figure out why those files didn't get removed/overwritten
by Snakemake when I re-ran everything.

>>>>

It looks like one result per parameter set is left over from before I re-ran 
everything after reverting to the older silva version.
[Here's what the plot looked like with the newest (buggy) silva](https://github.com/SchlossLab/OptiFitAnalysis/blob/master/exploratory/2020-05/sub3_fit_all-seqs.md#fraction-of-sequences-that-map-to-the-reference).
Need to go back and figure out why those files didn't get removed/overwritten
by Snakemake when I re-ran everything.

Let's try a sanity check with open-reference -- should all be 1.

```{r fraction-mapped-open_fit-split}
optifit_split %>% 
  filter(method == 'open', tool == 'mothur', is.na(ref)) %>% 
  #group_by(dataset, ref_weight, ref_frac) %>% 
  ggplot(aes(x=ref_frac, y=fraction_mapped, color=ref_weight)) +
  geom_jitter(alpha = 0.5, width = 0.01, size=1) +
  facet_wrap("dataset", nrow=1) +
  ylim(0, 1) +
  labs(title="Sequences mapped during open-reference OptiFit",
       x='reference fraction',
       y='fraction mapped')
```

Did mothur's list file format change in the latest dev version?
